The quench action approach in finite integrable spin chains

### 2015-12-05 QAMC_draft/fs_qa_v7.tex
05/12/2015

We consider the problem of constructing the stationary state following a quantum quench, 
using the exact overlaps for finite size integrable models. 
We focus on the isotropic Heisenberg spin chain with initial state N\'eel or Majumdar-Ghosh (dimer),
although the proposed approach is valid for an arbitrary integrable model. 
We consider only those states which do not contain zero-momentum strings because the latter 
are affected by fictitious singularities that are very difficult to take into account. 
We show that the fraction of eigenstates that do not contain zero-momentum strings is vanishing in the thermodynamic limit.
Consequently, restricting to this part of the Hilbert space would lead to vanishing expectation values of local observables. 
It is, however, possible to reconstruct the asymptotic values by properly reweighing the expectations in the considered 
subspace at the price of introducing finite-size corrections. 
We also develop a Monte Carlo sampling of the Hilbert space which allows us to study larger systems. 
We accurately reconstruct the expectation values of the conserved charged and the root distributions in the stationary state, 
which turn out to match the exact thermodynamic results. 
The proposed method can be  implemented even in cases in which an analytic thermodynamic solution is not obtainable.

@@

However, this does not imply that the diagonal ensemble cannot be reconstructed  
from the eigenstates without zero-momentum strings and it is not in contrast 
with the previous quench action results in the thermodynamic limit \cite{wouters-2014A,pozsgay-2014A}.
Indeed, we show  that the correct diagonal ensemble 
sum rules can be recovered in the thermodynamic limit by appropriately 
reweighing the contribution of the finite-momentum strings eigenstates.

@@

Strikingly, after the reweighing, although for small chains violations of the conserved quantities 
sum rules are present, these violations vanish in the thermodynamic limit 
and the sum rules are restored. This implies that the only effect of the 
Hilbert space truncation is to introduce finite size scaling corrections. 
In the quench action language, this means that the eigenstates corresponding to non 
zero-momentum strings contain enough physical information about saddle point. 
This is numerically confirmed by extracting the so-called saddle point 
root distributions, which in the Bethe ansatz language fully characterize 
the diagonal ensemble averages in the thermodynamic limit. In the numerical  
 approach these are obtained from the histograms of the Bethe ansatz 
solutions sampled during the Monte Carlo. A part from finite size scaling 
corrections, we observe striking agreement with analytical results, at least 
for the first few root distributions.

@@

In this section we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
($XXX$) chain. Specifically, in subsection~\ref{sec:1.2} we discuss the structure of  
its eigenstates (Bethe states) and the associated Bethe equations. 
Subsection~\ref{sec:1.3} focuses on the string hypothesis 
and the so-called Bethe-Gaudin-Takahashi (BGT) equations. The form of the 
BGT equations in the thermodynamic limit is discussed in subsection~\ref{sec:1.4}. 
Finally, in subsection~\ref{sec:1.5} we provide the exact formulas for the 
local conserved charges of the model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The thermodynamic limit}
\label{sec:1.4}

@@

\subsection{Quench action reweighing}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.95\textwidth]{./draft_figs/full_vs_mc.pdf}
\end{center}
\caption{Energy density expectation values for a quench from N\'eel (a) and Majumdar-Ghosh state (b) obtained by means of the 
reweighing \eref{rewe}.
For the Majumdar-Ghosh state a quadratic fit (forcing the asymptotic value $Q_2^{(0)}=-5/8$) describes perfectly the reweighed 
data.
For the N\'eel state we also report the Monte Carlo data obtained in the next section, showing perfect agreement with the 
reweighed Bethe ansatz data. 
}
\label{fig:rew}
\end{figure}

The results obtained by reweighing the data in Figs. \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}
are shown in Fig. \ref{fig:rew} focusing on the conserved energy density for both the N\'eel and 
Majumdar-Ghosh initial states. 
It is evident that the data after reweighing approach a finite value for large $L$ in contrast with the bare vanishing values 
(cf. Figs.  \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}). 
It is, however, also clear that this procedure introduces some finite size corrections due to the restriction of the Hilbert space that is 
only justified in the thermodynamic limit. 
%
For the Majumdar-Ghosh state these corrections are monotonous and one can extrapolate with a quadratic fit in $1/L$
to infinite size, in order to reproduce the correct thermodynamic expectation (see Fig. \ref{fig:rew} panel (b)).
%
For the N\'eel initial state instead, the corrections to the scaling are not monotonous and an extrapolation 
based only on the data up to $L=38$ are inconclusive. 
In Fig. \ref{fig:rew} we plot on top of the exact Bethe ansatz data, also Monte Carlo results obtained by sampling the restricted 
Hilbert space (see next section). 
The Monte Carlo allows to consider larger system sizes, which turns out to be enough for a good extrapolation, as we
will discuss in the next section. 
We limit here to notice that the agreement between exact and Monte Carlo data is excellent, corroborating 
the correctness of both approaches.

Finally, it is worth stressing that although the Monte Carlo sampling is done only on the 
zero-momentum free Hilbert subspace, the algorithm does not suffer of the reweighing problems 
found in the exact method (see the preceding section), because the expectation values 
\eref{qamc-obs} are automatically normalised by the factor $N_{mcs}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Counting and string content of the eigenstates with nonzero N\'eel and 
Majumdar-Ghosh overlap}
\label{app-1}

Here we provide some exact combinatorial formulas for the total number of 
parity-invariant eigenstates of the $XXX$ chain having non-zero overlap with 
the N\'eel state and the Majumdar-Ghosh state. 
%We consider both the situations  
%with constrained and unconstrained string content and particle number (i.e., 
%total magnetization). 
In~\ref{app-1.1} we consider all possible parity-invariant 
eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
zero-momentum strings. Note that the result in~\ref{app-1.1} is only an upper 
bound, while the counting in~\ref{app-1.2} is exact. The strategy of the proof 
is the same as that used to count the number of solutions of the 
Bethe-Gaudin-Takahashi equations (see for instance Ref.~\cite{faddeev-1996}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Allowing the zero-momentum strings}
\label{app-1.1}

Here we prove that the total number of parity-invariant eigenstates $Z_{Neel}$ 
with, in principle, non-zero N\'eel overlap for a chain of length $L$ is given 
as 
%
\begin{equation}
\label{N-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
\end{equation}
%
We restrict ourselves to the situation with $L$ divisible by four. The strategy to 
prove~\eref{N-count} is to count all the possible parity-invariant BGT quantum numbers 
configurations (cf. section~\ref{sec:1.3}). Let us consider the sector with fixed number 
of particles $M$, and string content ${\mathcal S}=\{s_1,s_2,\dots,s_{M}\}$. Here $s_n$ is 
the number of $n$-strings, with the constraint $\sum_k ks_k=M$. One should stress that 
$M$ is the number of particles corresponding to {\it finite} solutions of the Bethe 
equations. The total number of particles is $L/2$, due to the fact that the N\'eel 
state has $S_T^z=0$. The remaining $L/2-M$ particles correspond to infinite solutions 
of the Bethe equations (see section~\ref{sec:1.2}). It is straightforward to check that the
total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{\mathcal S})$ 
in the $n$-string sector is given as 
%
\begin{equation}
\label{NnLS}
{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{M}t_{nm}s_m\Big\rfloor,
\end{equation}
%
where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
quantum number pairs as     
%
\begin{equation}
\label{NLS}
{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{M} B\left({\mathcal N}_m,\left\lfloor
\frac{s_m}{2}\right\rfloor\right).
\end{equation}
%
Here the product is because each string sector is treated independently, while the 
factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
only half of them have to be specified. Note that in each $n$-string sector only one 
zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
that $s_m$ is odd (even) only if this zero momentum string is (not) present.

We now proceed to consider the string configurations with fixed particle number $0\le\ell
\le M$ and fixed number of strings $1\le q\le M/2$. Note that the maximum allowed string 
length is $M/2$ because of parity invariance. Note also that in determining $q$, strings 
of different length are treated equally, i.e., $q=\sum_m s_m$. For a given fixed pair 

@@

where the sum is over the string content $\{s_m\}_{m=1}^M$ compatible with the constraints 

@@

values of $\ell=2k$ with $k=0,1,\dots,\ell/2$. Note that the sum is over $\ell$ even 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Excluding the zero-momentum strings}
\label{app-1.2}

Here we demonstrate that the total number of eigenstates $\widetilde Z_{Neel}(L)$ 
with nonzero N\'eel overlap, after excluding the zero-momentum strings, is given as 
%
\begin{equation}
\label{result}
\widetilde Z_{Neel}(L)=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
\end{equation}
One should first observe that in a generic $M$-particle eigenstate of the $XXX$ chain, 
due to parity invariance, only $n$-strings with length $n\le M/2$ are allowed. Also, the 
string content can be written as $\widetilde{\mathcal S}\equiv\{\tilde s_1,\dots,\tilde 
s_{M/2}\}$, i.e., $\tilde s_m=0$ $\forall m>M/2$. Due to the parity invariance 
one has that $\tilde s_m$ is always even. Clearly one has $\sum_{m=1}^{M/2}m \tilde 
s_m=M$. Finally, the total number of parity-invariant quantum numbers $\widetilde{
\mathcal N}_n$ in the $n$-string sector is given as  
%
\begin{equation}
\widetilde{\mathcal N}_n(L,\widetilde{\mathcal S})=\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{M/2}t_{nm}\tilde s_m.
\end{equation}
%
The proof now proceeds as in the previous section. One defines the total number of eigenstates 
with nonzero N\'eel overlap in the sector with fixed $\ell$ particles and $q$ different 
string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straightforward to show that 
$\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
%
\begin{equation}
\label{NpLlq-1}
\widetilde{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q/2-1}B\Big(\frac{L}{2}-q+s,s\Big)\widetilde
{\mathcal N}'\Big(L-2q,\frac{\ell-q}{2},\frac{q}{2}-s\Big),
\end{equation}
% 
with the constraint
%
\begin{equation}
\widetilde{\mathcal N}'(L,1,1)=\frac{L}{2}-1. 
\end{equation}
%
The solution of~\eref{NpLlq-1} is given as 
%
\begin{equation}
\widetilde{\mathcal N}'(L,\ell,q)=\frac{L-2\ell+2}{L-\ell+2}B\Big(\frac{L-\ell}{2}+1,q\Big)
B\Big(\frac{\ell}{2}-1,\frac{q}{2}-1\Big).
\end{equation}
%
After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
the total number of eigenstates with nonzero N\'eel overlap at fixed number of 
particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
%
\begin{equation}
\label{Neel-fi}
\widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
B\Big(\frac{L}{2},\frac{\ell}{2}-1\Big).
\end{equation}
%
Summing over $\ell$ one obtains~\eref{result}. Similar to~\eref{p-inv-mg} the total number 
of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the Majumdar-Ghosh state 
is obtained from~\eref{Neel-fi} by replacing $\ell\to L/2$, to obtain 
%
\begin{equation}
\label{mg-fi}
\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},\frac{L}{4}-1
\Big). 
\end{equation}
%
Interestingly, using~\eref{p-inv-mg} and~\eref{mg-fi}, one obtains that the ratio 
$\widetilde Z_{MG}/Z_{MG}$ is given as 
%
\begin{equation}
\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
\end{equation}
%

@@

In this section we provide exact diagonalization results for the overlaps between the 
N\'eel state and the Majumdar-Ghosh (MG) state and all the eigenstates of the Heisenberg 
spin chain with $L=12$ sites. For the eigenstates without zero-momentum strings, we 
also provide the overlaps obtained using the string hypothesis~\eref{Neel-ov}\eref{mg-ov}. 
This allows to check the validity of the string hypothesis when calculating overlaps. 
Moreover, this also provides a simple check of the counting formula~\eref{result}.

>>>>

We consider the problem of constructing the stationary state following a quantum quench, 
using the exact overlaps for finite size integrable models. 
We focus on the isotropic Heisenberg spin chain with initial state N\'eel or Majumdar-Ghosh (dimer),
although the proposed approach is valid for an arbitrary integrable model. 
We consider only those states which do not contain zero-momentum strings because the latter 
are affected by fictitious singularities that are very difficult to take into account. 
We show that the fraction of eigenstates that do not contain zero-momentum strings is vanishing in the thermodynamic limit.
Consequently, restricting to this part of the Hilbert space would lead to vanishing expectation values of local observables. 
It is, however, possible to reconstruct the asymptotic values by properly reweighting the expectations in the considered 
subspace at the price of introducing finite-size corrections. 
We also develop a Monte Carlo sampling of the Hilbert space which allows us to study larger systems. 
We accurately reconstruct the expectation values of the conserved charged and the root distributions in the stationary state, 
which turn out to match the exact thermodynamic results. 
The proposed method can be  implemented even in cases in which an analytic thermodynamic solution is not obtainable.

@@

However, this does not imply that the diagonal ensemble cannot be reconstructed  
from the eigenstates without zero-momentum strings and it is not in contrast 
with the previous quench action results in the thermodynamic limit \cite{wouters-2014A,pozsgay-2014A}.
Indeed, we show  that the correct diagonal ensemble 
sum rules can be recovered in the thermodynamic limit by appropriately 
reweighting the contribution of the finite-momentum strings eigenstates.

@@

Strikingly, after the reweighting, although for small chains violations of the conserved quantities 
sum rules are present, these violations vanish in the thermodynamic limit 
and the sum rules are restored. This implies that the only effect of the 
Hilbert space truncation is to introduce finite size scaling corrections. 
In the quench action language, this means that the eigenstates corresponding to non 
zero-momentum strings contain enough physical information about saddle point. 
This is numerically confirmed by extracting the so-called saddle point 
root distributions, which in the Bethe ansatz language fully characterize 
the diagonal ensemble averages in the thermodynamic limit. In the numerical  
 approach these are obtained from the histograms of the Bethe ansatz 
solutions sampled during the Monte Carlo. A part from finite size scaling 
corrections, we observe striking agreement with analytical results, at least 
for the first few root distributions.

@@

In this section we review some Bethe ansatz results for the spin-$\frac{1}{2}$ Heisenberg 
($XXX$) chain. Specifically, in subsection~\ref{sec:1.2} we discuss the structure of  
its eigenstates (Bethe states) and the associated Bethe equations. 
Subsection~\ref{sec:1.3} focuses on the string hypothesis 
and the so-called Bethe-Gaudin-Takahashi (BGT) equations. 
The form of the BGT equations in the thermodynamic limit is discussed in subsection~\ref{sec:1.4}. 
In subsection~\ref{app-1} we provide some combinatorial formulas for the total 
number of the so-called parity-invariant eigenstates. The latter are the only eigenstates 
having non-zero overlap with the N\'eel and Majumdar-Ghosh states. 
Finally, in subsection~\ref{sec:1.5} we provide the exact formulas for the 
local conserved charges of the model.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Thermodynamic Bethe Ansatz}
\label{sec:1.4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Counting and string content of the eigenstates with nonzero N\'eel and 
%Majumdar-Ghosh overlap}
\subsection{Counting and string content of parity-invariant eigenstates}
\label{app-1}

Here we provide some exact combinatorial formulas for the total number of 
parity-invariant eigenstates of the $XXX$ chain, which are the only eigenstates 
having, in principle, non-zero overlap with the N\'eel state and the 
Majumdar-Ghosh state~\cite{brockmann-2014}. 
Parity-invariant eigenstates correspond to solutions of the Bethe equations 
containing only pairs of rapidities with opposite sign. In turn, these  
eigenstates are in one-to-one correspondence with parity-invariant BGT quantum number 
configurations. %In~\ref{app-1.1} we consider all possible parity-invariant 
%eigenstates, whereas in~\ref{app-1.2} we exclude the eigenstates containing 
%zero-momentum strings.

For simplicity we restrict ourselves 
to the situation with $L$ divisible by four. The strategy of the proof is the 
same as that used to count the number of solutions of the Bethe-Gaudin-Takahashi 
equations (see for instance Ref.~\cite{faddeev-1996}).  Specifically, the idea 
is to count all the possible BGT quantum numbers configurations corresponding 
to parity-invariant eigenstates (cf. section~\ref{sec:1.3}).

We anticipate that the total number of parity-invariant eigenstates $Z_{Neel}$ 
for a chain of length $L$ is given as 
%
\begin{equation}
\label{N-count}
Z_{Neel}=2^{\frac{L}{2}-1}+\frac{1}{2}B\Big(\frac{L}{2},\frac{L}{4}\Big)+1. 
\end{equation}
%
On the other hand, after excluding the zero-momentum strings one obtains 
%
\begin{equation}
\label{N-count-nz}
\widetilde Z_{Neel}=B\Big(\frac{L}{2},\frac{L}{4}\Big). 
\end{equation}
%
Note that~\eref{N-count} is only an upper bound for the number of eigenstates 
with non-zero N\'eel overlap, while~\eref{N-count-nz} is exact. Before 
proceeding, we should stress that the total number of particles  
in the eigenstates having non-zero overlap with the N\'eel and Majumdar-Ghosh 
states is fixed to $L/2$, due to the fact that for both states one has $S_T^z=0$. 
However, since the N\'eel state is not $SU(2)$ invariant, eigenstates with 
non-zero N\'eel overlap can contain infinity rapidities. Thus, one has to 
consider all the possible sectors with $L/2=\ell+N_{\infty}$, and $\ell$ 
($N_\infty$) the number of finite (infinite) rapidities. Notice that this 
is different for the Majumdar-Ghosh state, for which only the parity-invariant 
eigenstates in the sector with $\ell=L/2$ have to be considered (see below).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\underline{Parity-invariant states with $\ell$ finite rapidities.}}
\label{app-1.1}

Let us first consider the eigenstate sector with fixed number of finite rapidities 
$\ell$, the remaining $L/2-\ell$ ones being infinite (see section~\ref{sec:1.2}). 
Let us denote the associate string content as ${\mathcal S}=\{s_1,s_2,\dots,
s_{\ell}\}$. Here $s_n$ is the number of $n$-strings, with the constraint 
$\sum_k ks_k=\ell$. 
It is straightforward to check that 
the total number of parity-invariant quantum number pairs ${\mathcal N}_n(L,{
\mathcal S})$ in the $n$-string sector is given as 
%
\begin{equation}
\label{NnLS}
{\mathcal N}_n(L,{\mathcal S})=\Big\lfloor\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{\ell}t_{nm}s_m\Big\rfloor,
\end{equation}
%
where $t_{nm}\equiv 2\textrm{Min}(n,m)-\delta_{n,m}$. Thus, the number of parity-invariant 
eigenstates of the $XXX$ chain ${\mathcal N}(L,{\mathcal S})$ compatible with string content 
${\mathcal S}$ is obtained by choosing in all the possible ways the associated parity-invariant 
quantum number pairs as     
%
\begin{equation}
\label{NLS}
{\mathcal N}(L,{\mathcal S})=\prod_{m=1}^{\ell} B\left({\mathcal N}_m,\left\lfloor
\frac{s_m}{2}\right\rfloor\right).
\end{equation}
%
Here the product is because each string sector is treated independently, while the 
factor $1/2$ in $s_m/2$ is because since all quantum numbers are organized in pairs, 
only half of them have to be specified. Note that in each $n$-string sector only one 
zero momentum (i.e., zero quantum number) string is allowed, due to the fact that 
repeated solutions of the BGT equation are discarded. Moreover, from~\eref{NnLS} one has 
that $s_m$ is odd (even) only if this zero momentum string is (not) present.

We now proceed to consider the string configurations with fixed particle number $\ell\le 
L/2$ and fixed number of strings $1\le q\le\ell$. Note that due to parity invariance 
$\ell$ must be even. 
Also, in determining $q$ strings of different length are treated equally, i.e., 
$q=\sum_m s_m$. For a given fixed pair 

@@

where the sum is over the string content $\{s_m\}_{m=1}^\ell$ compatible with the constraints 

@@

values of $\ell=2k$ with $k=0,1,\dots,L/2$. Note that the sum is over $\ell$ even 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{\underline{Excluding the zero-momentum strings.}}
\label{app-1.2}

One should first observe that for the generic eigenstate of the $XXX$ chain with 
$\ell$ finite rapidities, due to parity invariance and the exclusion of zero-momentum 
strings, only $n$-strings with 
length $n\le \ell/2$ are allowed. Also, the string content can be written as 
${\mathcal S}\equiv\{s_1,\dots,s_{\ell/2}\}$, i.e., $s_m=0$ $\forall m>
\ell/2$. Due to the parity invariance one has that $s_m$ is always even. Clearly 
one has $\sum_{m=1}^{\ell/2}m s_m=\ell$. Finally, the total number of 
parity-invariant quantum numbers $\widetilde{\mathcal N}_n$ in the $n$-string 
sector is given as  
%
\begin{equation}
\widetilde{\mathcal N}_n(L,{\mathcal S})=\frac{L}{2}-\frac{1}{2}
\sum_{m=1}^{\ell/2}t_{nm} s_m.
\end{equation}
%
The proof now proceeds as in the previous section. One defines the total number of eigenstates 
with nonzero N\'eel overlap in the sector with fixed $\ell$ finite rapidities and $q$ different 
string types as $\widetilde{\mathcal N}'(L,\ell,q)$. It is straightforward to show that 
$\widetilde{\mathcal N}'(L,\ell,q)$ obeys the recursive relation
%
\begin{equation}
\label{NpLlq-1}
\widetilde{\mathcal N}'(L,\ell,q)=\sum_{s=0}^{q/2-1}B\Big(\frac{L}{2}-q+s,s\Big)\widetilde
{\mathcal N}'\Big(L-2q,\frac{\ell-q}{2},\frac{q}{2}-s\Big),
\end{equation}
% 
with the constraint
%
\begin{equation}
\widetilde{\mathcal N}'(L,1,1)=\frac{L}{2}-1. 
\end{equation}
%
The solution of~\eref{NpLlq-1} is given as 
%
\begin{equation}
\widetilde{\mathcal N}'(L,\ell,q)=\frac{L-2\ell+2}{L-\ell+2}B\Big(\frac{L-\ell}{2}+1,q\Big)
B\Big(\frac{\ell}{2}-1,\frac{q}{2}-1\Big).
\end{equation}
%
After summing over the allowed values of $q=2k$ with $k=1,2,\dots,\ell/2$ one obtains 
the total number of eigenstates with nonzero N\'eel overlap at fixed number of 
particles $\ell$ $\widetilde Z_{Neel}'(L,\ell)$ as 
%
\begin{equation}
\label{Neel-fi}
\widetilde Z_{Neel}'(L,\ell)=B\Big(\frac{L}{2},\frac{\ell}{2}\Big)-
B\Big(\frac{L}{2},\frac{\ell}{2}-1\Big).
\end{equation}
%
by summing over $\ell$ one obtains~\eref{N-count-nz}. Similar to~\eref{p-inv-mg} the 
total number of eigenstates $\widetilde Z_{MG}$ having non-zero overlap with the 
Majumdar-Ghosh state is obtained from~\eref{Neel-fi} by replacing $\ell\to L/2$, to obtain 
%
\begin{equation}
\label{mg-fi}
\widetilde Z_{MG}=B\Big(\frac{L}{2},\frac{L}{4}\Big)-B\Big(\frac{L}{2},\frac{L}{4}-1
\Big). 
\end{equation}
%
Interestingly, using~\eref{p-inv-mg} and~\eref{mg-fi}, one obtains that the ratio 
$\widetilde Z_{MG}/Z_{MG}$ is given as 
%
\begin{equation}
\frac{\widetilde Z_{MG}}{Z_{MG}}=\frac{4}{4+L}. 
\end{equation}
%

\subsection{Quench action reweighting}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.95\textwidth]{./draft_figs/full_vs_mc.pdf}
\end{center}
\caption{Energy density expectation values for a quench from N\'eel (a) and Majumdar-Ghosh state (b) obtained by means of the 
reweighting \eref{rewe}.
For the Majumdar-Ghosh state a quadratic fit (forcing the asymptotic value $Q_2^{(0)}=-5/8$) describes perfectly the reweighed 
data.
For the N\'eel state we also report the Monte Carlo data obtained in the next section, showing perfect agreement with the 
reweighed Bethe ansatz data. 
}
\label{fig:rew}
\end{figure}

The results obtained by reweighting the data in Figs. \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}
are shown in Fig. \ref{fig:rew} focusing on the conserved energy density for both the N\'eel and 
Majumdar-Ghosh initial states. 
It is evident that the data after reweighting approach a finite value for large $L$ in contrast with the bare vanishing values 
(cf. Figs.  \ref{fig1:Neel-sr} and \ref{fig2:dimer-sr}). 
It is, however, also clear that this procedure introduces some finite size corrections due to the restriction of the Hilbert space that is 
only justified in the thermodynamic limit. 
%
For the Majumdar-Ghosh state these corrections are monotonous and one can extrapolate with a quadratic fit in $1/L$
to infinite size, in order to reproduce the correct thermodynamic expectation (see Fig. \ref{fig:rew} panel (b)).
%
For the N\'eel initial state instead, the corrections to the scaling are not monotonous and an extrapolation 
based only on the data up to $L=38$ are inconclusive. 
In Fig. \ref{fig:rew} we plot on top of the exact Bethe ansatz data, also Monte Carlo results obtained by sampling the restricted 
Hilbert space (see next section). 
The Monte Carlo allows to consider larger system sizes, which turns out to be enough for a good extrapolation, as we
will discuss in the next section. 
We limit here to notice that the agreement between exact and Monte Carlo data is excellent, corroborating 
the correctness of both approaches.

Finally, it is worth stressing that although the Monte Carlo sampling is done only on the 
zero-momentum free Hilbert subspace, the algorithm does not suffer of the reweighting problems 
found in the exact method (see the preceding section), because the expectation values 
\eref{qamc-obs} are automatically normalised by the factor $N_{mcs}$.

@@

In this section we provide exact diagonalization results for the overlaps between the 
N\'eel state and the Majumdar-Ghosh (MG) state and all the eigenstates of the Heisenberg 
spin chain with $L=12$ sites. For the eigenstates without zero-momentum strings, we 
also provide the overlaps obtained using the string hypothesis~\eref{Neel-ov}\eref{mg-ov}. 
This allows to check the validity of the string hypothesis when calculating overlaps. 
Moreover, this also provides a simple check of the counting formula~\eref{N-count-nz}.
